Empirical Bayes analysis for detection of gene heterosis in RNAseq data

### 2014-12-18 ebayes_rnaseq_heterosis.tex
added blinding command

@@

\author{Jarad Niemi$^*$\email{niemi@iastate.edu}, 
Eric Mittman, 
Will Landau, and 
Dan Nettleton \\
Department of Statistics, Iowa State University, Ames, Iowa, U.S.A.}

@@

\section*{Acknowledgements}

The authors thank Andrew Lithio for help in implementing our model in {\tt ShrinkBayes}. Research reported in this publication was supported by National Institute of General Medical Sciences of the National Institutes of Health under award number R01GM109458. The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.

>>>>

\newcommand{\blind}{1} % 0 = not blind, 1 = blind

@@

\if0\blind{
\author{Jarad Niemi$^*$\email{niemi@iastate.edu}, 
Eric Mittman, 
Will Landau, and 
Dan Nettleton \\
Department of Statistics, Iowa State University, Ames, Iowa, U.S.A.}
} \fi

@@

\if0\blind{
\section*{Acknowledgements}

The authors thank Andrew Lithio for help in implementing our model in {\tt ShrinkBayes}. Research reported in this publication was supported by National Institute of General Medical Sciences of the National Institutes of Health under award number R01GM109458. The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
} \fi
